Data Analysis and Modeling

### 2018-10-28 scripts/4_data_analysis.Rmd
Add: Knn imputation method.

>>>>

  kimp_df <- knnImputeWrap(ltr_df = ltr_df, 
                           str_df = str_tdf,
                           knns = c(3, 5, 7))

  imp_df$ltr_imp_revenueK <- kimp_df$year[match(imp_df$property_id,
                                               kimp_df$property_id)]
  imp_df <- imp_df %>%
    rename(ltr_imp_revenueH = ltr_imp_revenue) %>%
    mutate(ltr_imp_revenueK = ((365-imp_dom)/365) * ltr_imp_revenueK,
           ltr_imp_revenue = .5 * (ltr_imp_revenueH + ltr_imp_revenueK),
           lir_hi = ltr_imp_revenue * 1.15,
           lir_lo = ltr_imp_revenue * .85)
